---
title: "R for Data Science Exercises"
author: "Dave Anderson"
date: "September 23, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
```

#R for Data Science Exercises (Assignment 2)

#3.5.1 #2 and 3
2)What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?
```{r fig.height = 3}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))
```
*Answer: The empty grids represent areas where that combination of variables does not exist. Same with empty spots in this plot. Example: There are no cars with 4 wheel drive and a 5 cylinder engine.*

\vspace{12pt}

3)What plots does the following code make? What does . do?

```{r fig.height = 3}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```
*Answer: The period is an empty placeholder in the rows or columns spot. It is similar when we are using [3,] to select a specific row. It is letting you sort your facets by row or column, vertical vs. horizontal*

\newpage
#3.6.1 #6

```{r fig.height = 3 }
#1
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(mapping = aes(x = displ, y = hwy), se = FALSE)

#2
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(mapping = aes(x = displ, y = hwy, group = drv), se = FALSE)

#3
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_smooth(mapping = aes(x = displ, y = hwy, group = drv, color = drv), se = FALSE)


#4
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_smooth(mapping = aes(x = displ, y = hwy), color = "blue", se = FALSE)

```

\newpage
```{r fig.height=3}
#5
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(colour = drv)) +
  geom_smooth(aes(linetype = drv), se = FALSE)

#6
ggplot(mpg, aes(x = displ, y = hwy)) +
   geom_point(size = 4, color = "white") +
   geom_point(aes(colour = drv))

```
\newpage

#5.2.4 #1,2,3,4

1) Find all flights that:

```{r}
flights <- nycflights13::flights
#1 Had an arrival delay of two or more hours
TWo_hour_delay <- filter(flights, arr_delay >= 120)

#2 Flew to Houston (IAH or HOU)
Houston <- filter(flights, dest == "IAH"| dest == "HOU")

#3 Were operated by United, American, or Delta
United_American_Delta <- filter(flights, carrier %in% c("AA", "DL", "UA"))

#4 Departed in Summer
Summer <- filter(flights, month >= 7 & month <= 9)

#5 Arrived more than two hours late, but didn't leave late
arrive_delay <- filter(flights, arr_delay >= 120 & dep_delay <= 0)

#6 Were delayed by at least an hour, but made up over 30 minutes in flight
quick_fly <- filter(flights, dep_delay >= 60, arr_delay <= 30)

#7 Departed between midnight and 6am (inclusive)
late_flight <- filter(flights, dep_time >= 0 & dep_time <= 600)
```


2) Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?

*Answer: between() simply allows us to filter data between two values. It would have been useful for the codes in problems 4 and 7. Simplified codes:* 
```{r}
#4
Summer <- filter(flights, between(month, 7, 9))

#7
late_flight <- filter(flights, between(dep_time, 0, 600))
```

3) How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

```{r}
missing <- filter(flights, is.na(dep_time))
```

*Answer: These rows are also missing arrival times, delay times, and flight times. These rows probably represent canceled flights.*

4) Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)

*Answer: NA ^ 0 is not missing because anything to the 0 power, even NA, has an output of 1. NA | TRUE will read as TRUE. Similarly, anything and FALSE will read as FALSE. NA times 0 reads as NA because if the missing spot read as infinity, the result would read as not a number.*
